% !TeX spellcheck = en_GB
\section{Haukeliseter Site}\label{sec:dim:site}
% and some more
%\subsection{Measurement site and climate}
Haukeliseter, shown in \Cref{fig:site} is a mountain plateau \SI{991}{\m} above sea level, located in the Norwegian county 'Telemark' (\ang{59.81}\,N, \ang{7.21}\,E, \Cref{fig:site}). The meteorological station measures precipitation, temperature, snow depth and wind and is operated by the Norwegian Meteorological Institute. It has served as a measurement site for snow accumulation since the winter of 2010/2011 \citep{wolff_new_2010} and serves as a WMO station. 
\\
%%% images measurement site %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{./images_tex/site_Norway_map}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
The study site is surrounded by mountain tops being \SIrange{100}{500}{\metre} higher than the flat area. As seen in \Cref{fig:site:kartverket} Haukeliseter is more open to the south and the south-west and the closest mountain top (situated to the NE) has an altitude of \SI{1162}{\metre} above sea level. The mountains to the west and north exceed elevations of \SI{1600}{\metre} above sea level.
\\
%%% image instrument setting @ Haukeli %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{./images_tex/instruments_setting}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent
A detailed setting of the measurement site is shown in \Cref{fig:inst_setting}. The precipitation sensors are perpendicular to the predominant wind. Additional measurements of other meteorological parameters such as temperature, wind, and pressure are used to connect the large-scale weather situation with the local measurements. The data is provided by weather- and climate data-server from Met-Norway \citep{eklima_norwegian_2016}, where the temperature is measured at double fence height. The hourly value of temperature is represented by the last minute value of the previous hour measurement. The \SI{10}{\metre} wind is measured by an ultrasonic wind sensor from Gill, mounted at the tower close to the double fence. Wind data is obtained from \citet{eklima_norwegian_2016} and represents \SI{10}{\minute} averages from the last \SI{10}{\minute} of an hour.
%In a study by \citet{wolff_derivation_2015} the wind-induced under-catch of solid precipitation is determined. Dependent on the kind of precipitation the wind plays different roles in the amount of accumulation. For temperatures below \SI{-2}{\celsius} the wind speed influences the falling snow. Where less precipitation can be observed at higher wind speeds or more precipitation can be measured if too much is blown into the gauge. The catch ratio between the standard Geonor precipitation gauge and the Double Fence - Geonor shows, that only \SI{80}{\percent} of solid precipitation are observed at wind speeds of \SI{2}{\mPs} and only \SI{40}{\percent} at \SI{5}{\mPs}, \citet[Figure 5 in][]{wolff_derivation_2015}. The double fence gauge is more accurate than the single fence and is used as the reference gauge. A further description of the double fence is found in \Cref{sec:dofe}. 
%\textcolor{red}{Steve: Should make some reference here to the vertical profile of observations needed to evaluate MEPS.  Me: What exactly does he mean?}. 
%Nevertheless, this shows the need of a combination of ground-based observations together with an optimal estimation retrieval to verify the accuracy of MEPS. \citet{wolff_derivation_2015} introduced an adjustment function for the Geonor double fence, so that different precipitation under certain wind speeds are presented correctly and can be used as confidential data. 
% \\ 
% \\
%
%
%
\newpage
\section{Climate at Haukeliseter}\label{sec:dim:dec_obs}
The general climate at Haukeliseter can be defined with the updated K\"oppen-Geiger climate types presented in \citet{peel_updated_2007}. Figure 8 in \citet{peel_updated_2007} show, that Haukeliseter may lay in a transition zone and can be categorized as ET, a polar tundra climate type (hottest month temperature T$_{hot}\ge$ \SI{0}{\celsius}) or as Dfc, a cold climate without dry season and cold summers. 
\\
Haukeliseter presents a typical Norwegian climate condition. At the measurement site, frequent snow events combined with high wind speeds are observed during a six to seven month winter period. In addition, a snow amount of about two to three meter can be expected, where \SI{50}{\percent} of the yearly precipitation is frozen \citep{wolff_derivation_2015}. 
\\
The mean wind direction (\Cref{fig:inst_setting}) for solid precipitation is from the west/east with maximum wind speed above \SI{15}{\mPs}, observed during a 10-year winter period at a nearby station \citep{wolff_derivation_2015}. 
\\
\Cref{fig:DecObs} shows the observations at the Haukeliseter site during December 2016.
In \Cref{fig:DecObs}, the green dashed line (\SI{-6}{\celsius}) represents the 30-year climate temperature in December \citep[\numrange{1961}{1990},][]{eklima_norwegian_2016}. 
% mean temperature in Dec was -1.1°C, climate = -6 --> dT = 4.9°C
December 2016 was warmer with an anomaly of +\SI{4.9}{\kelvin} above the climate mean. 
% total precipitation in Dec is 239.9mm, climate = 85mm --> dRR = 154.9
In December 2016, the precipitation was \SI{200}{\percent} higher than the climate mean. This difference could be associated with the new installation of the double fence - Geonor gauge at Haukeliseter. \citet[][Figure 5]{wolff_derivation_2015} shows that single fence precipitation gauges underestimate the amount of precipitation with approximately \SI{80}{\percent} during high wind speed events. The double fence gauge was not installed before 2010/2011, this might have led to an observation of too little precipitation at Haukeliseter during winter and leading to incorrect climate statistic.
% total precipitation during 21.-26.12. is 73 mm, total is 239.9mm --> 30.4%
The precipitation observed in the period of \num{21} to \SI{26}{\dec} were \SI{30}{\percent} of the total accumulated precipitation in December 2016. Furthermore, a maximum \SI{10}{\metre} wind speed of \SI{19}{\mPs} was observed in this period, which is considered as a gale. %a slight storm (\Cref{sec:loc_obs} and \Cref{tab:wind}).
%%% images December observation %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{./images_tex/site_Dec_obs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%