% !TeX spellcheck = en_GB
% ************************** Thesis Acknowledgements **************************

\begin{acknowledgement}   
	\noindent
	First and foremost, I would like to thank my supervisor, Richard Moore, for helpful discussions %, good guidance, feedback, 
	and giving me the opportunity to work with an interesting thesis. I would also like to thank my co-supervisor, Steve Cooper, for all the help with the optimal estimation retrieval, %the possibility to travel to Kiruna to learn more about the instrumentation, 
	good guidance and scientific discussions. A big thank goes to Bj\o rg Jenny Kokkvoll Engdahl for all the help to understand the ensemble prediction model and for helping me with miscellaneous questions I had throughout the year. I would also like to thank Kirstin Kr\"uger for her large effort in giving me constructive and detailed feedback on my scientific writing, and discussing results in the last minute. 
	\\
	I want to thank my fellow students at MetOs for a nice environment and good social and professional conversations. I also want to thank all the other friends I met during my studies in Germany and during my exchange at UNIS. %especially Roxana Cremer, Maria Hammarbäck, and Annceline Lemme. 
	It would not have been the same without you. %which would not have been so exciting without you. 
	%     \\
	%     Thank you goes to Roxana Cremer, Maria Hammarbäck, and Annceline Lemme, who helped me to improve my master thesis by cross reading and giving feedback.
	\\
	A very special thank you goes to all my good old friends and my family in Germany, who were always there for me and have supported and encouraged my choices all times. Last but not least, thanks to Dag \AA sb{\o} for proofreading, scientific discussions and listening to my complaints during time of frustration.
\end{acknowledgement}
